---
title: "Geocode"
output: html_document
---
There are many options for Geocoding. Like_____ but today we are going to look at Geocodio and its R interface rGeocodio
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

In order to install `rgeocodio` you will need to load the `devtools` package. Install it if you haven't already `install.packages("devtools")`. Once `devtools` is loaded run:
`devtools::install_github('hrbrmstr/rgeocodio')`.

geocodio uses...wait for it...an API! To get an API visit <https://dash.geocod.io/>. Then save it in your **Renviron**. Recall that you can do this by typing `usethis::edit_r_environ()` and saving your API code from the geocodio website.

We still need to authorize our API in our R session. Do so by running
```{r cars}
gio_auth(force = F)

```

`force` is an argumnet asking if you are **forcing** a new geocode API key to be set for the current environment. WHAT DOES THIS MEAN
## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
