---
title: "Tidyeval"
author: "Ethan Holdahl"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

# Unquoting: !! (Bang Bang)
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(pacman)
p_load(tidyverse, dplyr, rlang)
```

```{r, echo = TRUE}
cement = function(...){
  vars = ensyms(...)
  vars = map(vars, as.character)
  paste(vars, collapse = " ")
}

#What do you expect the function to do?
```
--
```{r, echo = TRUE}
cement(Van, Anne, Shankha, George)
```


---

# Unquoting: !! (Bang Bang)

```{r, echo = TRUE}
muggle = "David"

#What happens when we run cement(George, muggle)?
```
--
```{r, echo = TRUE}
cement(George, muggle)

#We use the Bang Bang operator to access the content of the variable
```
--
```{r, echo = TRUE}
cement(George, !!muggle)
```

```{r, echo = TRUE}
#We use rlang::qq_show() to see what your !! operators are doing
rlang::qq_show(cement(George, !!muggle))
```


---

# Using !!

```{r, echo = TRUE}
head(starwars)
```
--
```{r, echo = TRUE}
starwars %>%
  summarise(avg = mean(height, na.rm = TRUE))
```
---
#Using !!
```{r, echo=TRUE}
cols = c("height", "mass")
col = cols[[1]]
```
--
```{r, echo=TRUE}
rlang::qq_show(starwars %>%
  summarise(avg = mean(!!col, na.rm = TRUE)))
```
--
```{r, echo=TRUE}
starwars %>%
  summarise(avg = mean(!!col, na.rm = TRUE))
```
---
#Using !!: We need symbols!
```{r, echo = TRUE}
col = sym(cols[[1]])
```
--
```{r, echo=TRUE}
rlang::qq_show(starwars %>%
  summarise(avg = mean(!!col, na.rm = TRUE)))
```
--
```{r, echo=TRUE}
starwars %>%
  summarise(avg = mean(!!col, na.rm = TRUE))
```
---
# Tirple Bang !!! (splyce)

```{r, echo = TRUE}
#Triple Bang (splycing) is used for lists of quoted arguments
starwars %>%
  select(!!!cols)
```
--
```{r, echo=TRUE}
rlang::qq_show(starwars %>%
  select(!!!cols))
```
---
#Using quoting in functions: enquo()

```{r, echo = TRUE}
summarise_avg = function(data, col){
  col = enquo(col)
  data %>%
    summarise(avg = mean(!!col, na.rm = TRUE))
}
```
--
```{r, echo = TRUE}
summarise_avg(starwars, height)
summarise_avg(starwars, mass)
```
---
#Mapping
```{r, echo=TRUE}
map(syms(cols), summarise_avg, data = starwars)
```
---
#Using quosures

```{r, echo = TRUE}
#quosures capture the expression and the environment
#quo() is used when making your own quosure outside a function
quo(mass/height)

```
--
```{r, echo=TRUE}
my_mutate = function(df, var){
  n = 10
  var = enexpr(var)
  mutate(df, !!var)
}

df = tibble(x = 1)
n = 100
my_mutate(df, x+n)
```
---
#Changing the environment by using enquo()
```{r, echo=TRUE}
my_mutate = function(df, var){
  n = 10
  var = enquo(var)
  mutate(df, !!var)
}

df = tibble(x = 1)
n = 100
my_mutate(df, x+n)
```
---

# Hadley Wickham explaining Tidyeval
Probably much better that I just did. (spoilers: I used one of his examples)
[Video](https://www.youtube.com/watch?v=nERXS3ssntw)

---
#Hour long webinar on Tidyeval
(More spoilers: I used a couple more of this guy's examples)
[Longer Video](https://resources.rstudio.com/webinars/tidyeval)
