---
title: "Shiny"
author: "Ethan Holdahl"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

# Shiny!

What is shiny?

Shiny is a package that allows readers to chose input values that dynamically affect the rendered output. Basically, Shiny allows users who may know nothing about R to be able to pass their selected inputs into your functions and get reactive output. You can implement shiny into your markdown files, presentation slides, and even create an application and host that application on a website (so anyone can use it without even having R).

---

# Shiny in markdown files and slides

Using shiny in your markdown documents or slides is easy to implement! You only need to do 3 things:

First: add runtime: shiny to the setup of your page:
```{r, echo = TRUE, eval=FALSE}
---
title: "AMAZING SHINY markdown file"
author: "Ethan Holdahl"
output: html_document
runtime: shiny
---
```
---

# Shiny in markdown files and slides

Using shiny in your markdown documents or slides is easy to implement! You only need to do 3 things:

Second: load the shiny package
```{r, echo = TRUE, eval=FALSE}
library(pacman)
p_load(shiny)
```

---

# Shiny in markdown files and slides

Using shiny in your markdown documents or slides is easy to implement! You only need to do 3 things:

Third: Use \*Panel (I recomend inputPanel), \*Input, and render*

```{r, echo=TRUE, eval=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

Note: This is the example you get in the template if you create a new R Markdown Shiny document

---

# Shiny in markdown files and slides

That's it! Using shiny in markdown files or slides is like using a regular shiny app but with less parts required.

---

#Shiny Apps!

Garrett Grolemund has created a really fantastic [Tutorial Video](https://shiny.rstudio.com/tutorial/) which is 2.5 hours long but has bookmarks splitting the video up into 32 segments.

He has posted his [presentation materials on Github](https://github.com/rstudio-education/shiny.rstudio.com-tutorial).

Also I highly recommend checking out [The Shiny Gallery](https://shiny.rstudio.com/gallery/) which lets you see the app in action with the code backing it up.

